NHF1 General Read Sequence Figure Generation

### 2022-06-15 R/CS-BDeaminationSequenceAndPositionFigureGeneration.rmd
Restored custom plotting options
These options were lost during the refactoring for combined repetitions.

```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME,
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]])
}
```

>>>>

```{r CPD_mismatch_position_frequencies_by_read_length, fig.width = 9, fig.height = 5}
for (i in seq_along(CPDMismatchData)) {
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"),
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]], yAxisBreaks = c(0, 0.16, 0.32))
  plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"), posType = FIVE_PRIME,
                                           title = paste(c("CPD", titleCaseFiltering,
                                                           "C>T Mismatch Pos Freq", repNames[i]), collapse = ' '),
                                           zScoreTables = CPDMMFreqZScores[[i]], yAxisBreaks = c(0, 0.16, 0.32))
}
```

### 2022-06-15 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
Restored custom plotting options
These options were lost during the refactoring for combined repetitions.

>>>>

```{r CPD_mismatch_anchored_nucleotide_frequencies_filtered, fig.width = 11, fig.height = 8}
min3PrimeCutSiteDistance = 1
max3PrimeCutSiteDistance = 12

for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq[[i]], 
                                 title = paste(c("CPD", titleCaseFiltering,
                                                 "5' Anchored Nuc Freq", repNames[i]), collapse = ' '),
                                 yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                                 posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                                 expansionOffset = expansionOffset,
                                 minReadLength = min3PrimeCutSiteDistance, maxReadLength = max3PrimeCutSiteDistance)
}
```

### 2022-06-15 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Restored custom plotting options
These options were lost during the refactoring for combined repetitions.

>>>>

```{r CPD_sequence_frequencies_filtered, fig.width = 11, fig.height = 9}
minReadLength = 18
for (i in seq_along(CPDTGGSeqFreq)) {
  plotSequenceFrequencies(CPDTGGSeqFreq[[i]], title = paste("CPD TGG Frequencies", repNames[i]),
                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
                          showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = minReadLength)
}

for (i in seq_along(CPDCGASeqFreq)) {
  plotSequenceFrequencies(CPDCGASeqFreq[[i]], title = paste("CPD CGA Frequencies", repNames[i]),
                          expansionOffset = expansionOffset, showThreePrimeCutSite = TRUE,
                          showFivePrimeCutSite = TRUE, querySequences = c("CGA"), minReadLength = minReadLength)
}
```
